Title Goes Here

### 2023-01-06 analysis/paper/paper.qmd
add cleaning files

>>>>

# clean text
  emu_theses$text_clean <- emu_theses$text %>%
    str_replace_all("\\s", " ") %>%  ### remove all carriage return and newline characters
    str_squish() %>%
    str_replace_all("- ", "") %>%       ### remove all hyphens
    str_replace_all("[0-9]", "") %>%    ### remove all numbers
    str_replace_all(emu_theses$author_firstname[i], "") %>%   ### remove author first name
    str_replace_all(emu_theses$author_surname[i], "") %>%     ### remove author surname
    str_replace_all(emu_theses$title[i], "") %>%              ### remove title
    # str_replace_all("Claudiu Forgaci", "") %>%
    # str_replace_all("Bucharest: Between North and South", "") %>%
    str_replace_all("EMU", "")          ### remove common words
